Lab 13: Covariate Balancing and CBPS: Answers

### 2023-01-04 Lab 11 Missing data/Lab11_MissingData_AnswerKey.Rmd
Add files via upload

---
title: 'Lab 11 - Missing Data and Imputation'
author: "Eric Parajon"
header-includes:
  - \usepackage{enumerate}
  - \usepackage{graphicx}
output: pdf_document
---

@@

Below, use the function `na.omit()` to get rid of observations with missing values, then repeat the above `lm()` model with this new data.
```{r, eval = FALSE}
# subset with complete.cases to get complete cases
data_listwise <- na.omit(data_miss)
summary(data_listwise)

#let's create an lm with this model to compare to later iterations
#model Temp as your y, Ozone, Solar.R, and Wind as your x values
model_listwise <- lm(Temp ~ Ozone + Solar.R + Wind, data = data_listwise)

@@

```{r, eval = FALSE}
#make a copy of the data
data_recode <- data_miss

#uses if else statements to recode NA values as the mean of the rest of that column
#is.an()
data_recode$Ozone <- ifelse(is.na(data_recode$Ozone), 
                            mean(data_recode$Ozone, na.rm = TRUE),
                            data_recode$Ozone)

@@

data_recode$Temp <- ifelse(is.na(data_recode$Temp),
                            mean(data_recode$Temp, na.rm = TRUE),
                            data_recode$Temp)
#summarize
summary(data_recode)

@@

**Multiple Imputation**

Now multiple imputation, a super useful technique. First, we'll discuss `mice`. This package uses multivariate imputations to estimate missing values. What does this mean? Well, if a value is identified as missing, the package will then regress over the other variables and predict the various missing values. This is pretty cool. Further, using *multiple* imputations, or iterations of this process, instead of just one, helps us reduce uncertainty.

@@

#try this out with 25 iterations and 10 imputations
#select animputation method (try pmm) - what does it do differently?
mice_data_2 <- mice(data_miss, #call our data
                  m=_____, #number of multiple imputations
                  maxit=_____, #number of iterations
                  method = _____,
                  seed=500)

summary(mice_data_2)
```

So this is great, but then what do we do if we want to run a model? We have five data sets. One option is to pool the data this way:
```{r, eval = FALSE}
#pooling
model_mice <- with(mice_data,lm(Temp~ Ozone + Solar.R + Wind))
summary(pool(model_mice))
```
So mice is great. Let's also learn about Amelia II (my personal favorite, named after Amelia Earhart, because she is missing). Amelia is a little different because it assumes that your data is jointly distributed as multivariate normal. It uses the "expectation-maximization with bootstrapping" as an algorithm for imputation. The EM algorithm alternates between something called the expectation (E-step) and maximization (M-step) steps until it converges on values that were missing - it converges when the current and previous values are quite close (sounds a bit like Newton Raphson, no?). It brings in bootstraping by doing this process on multiple bootstrapped samples drawn from your original (and incomplete) data.

@@

```{r, message = FALSE}

#Load in packages
pacman::p_load(Amelia,
               lubridate,
               xtable)#For tables

@@

#let's run the model again, but this time using a for loop
models_amelia <- vector("list", 5)  #vector for our 5 newly imputed data sets

@@

#Pooling models (using mice)
summary(pool(models_amelia))

#Pulling into DF
pooled_df <- data.frame(summary(pool(models_amelia)))

#Displaying in table
xtable(pooled_df)

@@

Compare how models from mice, Amelia, and the above methods perform to our true data:
```{r, eval = FALSE}
#true model
summary(model_true)

@@

#Amelia
summary(pool(models_amelia))
```

@@

Try Amelia again, but this time let's use more of its functionality. Read in data from the `africa` package and examine its missingness. Then, using Amelia, impute missing values. Note that the dataset is cross-sectional by country, time series by year, and should have the `gdp_pc` variable specified as logged.

@@

```{r, eval = FALSE}
library(Amelia)
data("africa") #read in

#explore missingness
apply(africa, 2, function(x) sum(is.na(x))) #missingness by column

#use Amelia to generate 5 imputed datasets
#use ts and cs so imputation algerithem knows which variables represent countries and years

africa_imp <- amelia(x = __________, 
                     cs = __________ 
                     ts = __________
                     logs = "gdp_pc")

models_africa <- vector(__)
for(i in 1:length(africa_imp$imputations)){
  __________________________________) 
}

#report results, including standard errors

>>>>

---
title: 'Lab 11 - Missing Data and Imputation:Answers'
author: "Eric Parajon"
header-includes:
  - \usepackage{enumerate}
  - \usepackage{graphicx}
output: pdf_document
---

@@

Below, use the function `na.omit()` to get rid of observations with missing values
```{r}
# subset with complete.cases to get complete cases
data_listwise <- na.omit(data_miss)
summary(data_listwise)

#let's create an lm with this model to compare to later iterations
#model Temp as your y, Ozone, Solar.R, and Wind as your x values
model_listwise <- lm(Temp~ Ozone + Solar.R + Wind, data = data_listwise)

@@

```{r}
#make a copy of the data
data_recode <- data_miss

#uses if else statements to recode NA values as the mean of the rest of that column
data_recode$Ozone <- ifelse(is.na(data_recode$Ozone),
                            mean(data_recode$Ozone, na.rm = TRUE),
                            data_recode$Ozone)

@@

data_recode$Temp <- ifelse(is.na(data_recode$Temp),
                            mean(data_recode$Temp, na.rm = TRUE),
                            data_recode$Temp)

#summarize
summary(data_recode)

@@

**Multiple Imputation**
Now multiple imputation, a super useful technique. First, we'll discuss `mice`. This package uses multivariate imputations to estimate missing values. What does this mean? Well, if a value is identified as missing, the package will then regress over the other variables and predict the various missing values. This is pretty cool. Further, using *multiple* imputations, or iterations of this process, instead of just one, helps us reduce uncertainty.

@@

#try this out with 25 iterations and 10 imputations
#select animputation method (try pmm) - what does it do differently?
mice_data_2 <- mice(data_miss, #call our data
                  m=10, #number of multiple imputations
                  maxit=25, #number of iterations
                  method = "pmm",
                  seed=500)

summary(mice_data_2)

So this is great, but then what do we do if we want to run a model? We have five data sets. One option is to pool the data this way:
```{r}
#pooling
model_mice <- with(mice_data,lm(Temp~ Ozone + Solar.R + Wind))
summary(pool(model_mice))

```
So mice is great. Let's also learn about Amelia II (my personal favorite, named after Amelia Earhart, because she is missing). Amelia is a little different because it assumes that your data is jointly distributed as multivariate normal. It uses the "expectation-maximization with bootstrapping" as an algorithm for imputation. The EM algorithm alternates between something called the expectation (E-step) and maximization (M-step) steps until it converges on values that were missing - it converges when the current and previous values are quite close (sounds a bit like Newton Raphson, no?). It brings in bootstraping by doing this process on multiple bootstrapped samples drawn from your original (and incomplete) data.

@@

```{r}
#Load in packages
pacman::p_load(Amelia,
               lubridate)

@@

#let's run the model again, but this time using a for loop
models_amelia <- list() #create with as many elements that you know exist
#create a vector of type list of size five

@@

summary(pool(models_amelia))

@@

Compare how models from mice, Amelia, and the above methods perform to our true data:
```{r}
#true model
summary(model_true)

@@

#Amelia
summary(pool(models_amelia))

@@

Try Amelia again, but this time let's use more of its functionality. Read in data from the `africa` package and examine its missingness. Then, using Amelia, impute missing values. Not that the dataset is cross-sectional by country, time series by year, and should have the `gdp_pc` variable specified as logged.

@@

```{r}
library(Amelia)
data("africa") #read in

apply(africa, 2, function(x) sum(is.na(x))) #missingness by column

#use Amelia to generate 5 imputed datasets
#use ts and cs so imputation algs knows countries and years

africa_imp <- amelia(x = africa, cs = "country", ts = "year", logs = "gdp_pc")

models_africa <- list() 
for(i in 1:length(africa_imp$imputations)){
  models_africa[[i]] <- lm(gdp_pc ~ infl + trade + civlib + population,
                        data=africa_imp$imputations[[i]]) #why do we index like this?
}

summary(pool(models_africa))

#alternatively!
all_coefs <- sapply(models_africa, coef) #get coefs
all_ses <- sapply(models_africa, function(x) sqrt(diag(vcov(x)))) #get ses

mi.meld(q = all_coefs, se = all_ses, byrow = F) 
```

### 2023-01-04 Lab 12  Declare Design/Lab12_declaredesign_Answers.Rmd
Add files via upload

---
title: "Lab 12: Declare Design"
author: "Eric Parajon with code adapted from Colin Case"
output: pdf_document
header-include:
  - \usepackage{amsbsy}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, message = FALSE, warning = FALSE)
```

@@

df1 <- ________(
  N = ___, # Specify sample size. All subsequent variables need to have this 
           # number of observations for fabricate to work.
  draw_multivariate(c(___, ____) ~ _______( # Create variable names and simulate
    _______, # Specify sample size
    _________, # Specify means
    ______ = matrix(c(_,__,__,__), 2, 2))), # Specify covariance matrix.
                                              # Think carefully about the 
                                              # structure of the matrix 
                                              # and the values.
  Y = _______________
)

@@

```{r}
# Declare Model 1, specify the data argument
m1 <- ________________
```

@@

```{r}
# Declare Model 2
m2 <- 
  declare_model(
     N = 1000000, # Specify population size
    # Define potential_outcomes and specify formula with uncertainly around PATE
    potential_outcomes(Y ~ Z*________________) 
  )

@@

```{r}
# Declare Inquiry for PATE (Think -- what do we want to calculate)
inquiry2 <- declare_inquiry(__________________)
```

@@

```{r}
# Use declare_sample and specify S as completely random (complete_rs)
sample2 <- _______________________
```

@@

```{r}
# Define random assignment and specify Z as completely random with prob = 0.5
assignment2 <- __________________________
```

@@

```{r}
# Declare measurement, specify Y to reveal outcomes of assigned treatment
measurement2 <- ________________________
```

@@

```{r}
# Declare estimator
estimator1 <- __________________(_______, # Formula
                                term = ________, # Use term to identify which
                                                       # Variables you want to see
                                ___________) # Specify .method (what model?)
```

@@

```{r}
# Declare estimator
estimator2 <- declare_estimator(_______, # Specify formula
                                .method = ______________, # Specify measure
                                inquiry = _______) # Identify QOI
```

@@

From all the steps above, declare design creates values that need to be combined into a single element. To do this, you simply take the steps from above and add them to create the full design with + between each step. Be advised, the order of the steps matters! 
```{r}
# Create Design1 object by adding m1 and estimator1
design1 <- ___________________

# Create Design2 object by adding all steps for design2 above
design2 <- ___________________

@@

```{r}
# Use draw_data to view first ten rows of data for design1
___________________

# Use draw_data to view first ten rows of data for design2
___________________
```

@@

```{r}
# View Estimates for design1. Do they match expectations?
___________________

# View PATE for design2. Do they match expectations?
___________________
```

>>>>

---
title: "Lab 12: Declare Design: Answers"
author: "Eric Parajon with code adapted from Colin Case"
output: pdf_document
header-include:
  - \usepackage{amsbsy}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE)
```

@@

df1 <- fabricate(
  N = 500, # Specify sample size. All subsequent variables need to have this 
           # number of observations for fabricate to work.
  draw_multivariate(c(X_1, X_2) ~ mvrnorm( # Create variable names and simulate
    n = N, # Specify sample size
    mu = c(0, 4), # Specify means
    Sigma = matrix(c(1, 1.2, 1.2, 4), 2, 2))), # Specify covariance matrix.
                                              # Think carefully about the 
                                              # structure of the matrix 
                                              # and the values.
  Y = rnorm(500, mean = .5, sd = 10)*X_1 + rnorm(500, mean = 3, sd = 3)*X_2
)

@@

```{r}
# Declare Model 1, specify the data argument
m1 <- declare_model(data = df1)
```

@@

```{r}
# Declare Model 2
m2 <- 
  declare_model(
    N = 1000000, # Specify population size
    # Define potential_outcomes and specify formula with uncertainly around PATE
    potential_outcomes(Y ~ Z*rnorm(N, mean  = (0.1), sd = .2)) 
  )

@@

```{r}
# Declare Inquiry for PATE (Think -- what do we want to calculate)
inquiry2 <- declare_inquiry(PATE = mean(Y_Z_1 - Y_Z_0))
```

@@

```{r}
# Use declare_sample and specify S as completely random (complete_rs)
sample2 <- declare_sampling(S = complete_rs(N, n = 100))
```

@@

```{r}
# Define random assignment and specify Z as completely random with prob = 0.5
assignment2 <- declare_assignment(Z = complete_ra(100, prob = 0.5))
```

@@

```{r}
# Declare measurement, specify Y to reveal outcomes of assigned treatment
measurement2 <- declare_measurement(Y = reveal_outcomes(Y ~ Z))
```

@@

```{r}
# Declare estimator
estimator1 <- declare_estimator(Y ~ X_1+X_2, # Formula
                                term = c('X_1','X_2'), # Use term to identify which
                                                       # Variables you want to see
                                .method = lm) # Specify .method (what model?)
```

@@

```{r}
# Declare estimator
estimator2 <- declare_estimator(Y ~ Z, # Specify formula
                                .method = difference_in_means, # Specify measure
                                inquiry = "PATE") # Identify QOI
```

@@

From all the steps above, declare design creates values that need to be combined into a single element. To do this, you simply take the steps from above and add them to create the full design with + between each step. Be advised, the order of the steps matters! 
```{r}
# Create Design1 object by adding m1 and estimator1
design1 <- m1 + estimator1

# Create Design2 object by adding all steps for design2 above
design2 <- m2 + inquiry2 + sample2 + assignment2 + measurement2 + estimator2

@@

```{r}
# Use draw_data to view first ten rows of data for design1
draw_data(design1)[1:10,]

# Use draw_data to view first ten rows of data for design2
draw_data(design2)[1:10,]
```

@@

```{r}
# View Estimates for design1. Do they match expectations?
draw_estimates(design1)

# View PATE for design2. Do they match expectations?
draw_estimates(design2)

### 2023-01-04 Lab 13  CBPS/Lab13_covariatebalance_Answers.Rmd
Add files via upload

---
title: "Lab 13: Covariate Balancing and CBPS"
author: "Eric Parajon with code adapted from Colin Case"
output: html_document
header-include:
  - \usepackage{amsbsy}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \DeclareMathOperator*{\argmin}{argmin} % thin space, limits underneath in displays
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, message = FALSE, warning = FALSE)
```

@@

pacman::p_load(WeightIt,
               cobalt,
               tidyverse,
               stargazer,
               survey,
               jtools,
               CBPS,
               lmtest,
               sandwich)
# Load dataset Lalonde from cobalt package
data('lalonde', package = 'cobalt')

# Evaluate covariate balance on age, educ, married, nodegree, re74, and re75
________(treat ~ age + educ + married + nodegree + re74 + re75,
        data = lalonde, estimand = "ATT", m.threshold = .05)

@@

```{r}
# Estimate glm predicting treatment status
ps.mod <- glm(__________________)
# Create predictions from above model
ps <- ______(______, type = "response")
# View propensity scores
head(ps)
```

@@

```{r}
# Estimate and View model without weights
lalonde_model_noW <- lm(____ ~ _________, data=lalonde)
summary(lalonde_model_noW)
# Estimate and view model with weights
lalonde_model_w <- lm(____ ~ _________, data = lalonde, weights = weights)
summary(lalonde_model_w)
```

@@

```{r}
# Use weightit to calculate weights
W.out <- ________(______ ~ ____________________________,
        data = lalonde, estimand = "ATT", method = "ps")
W.out
```

@@

```{r}
# Re-examine covariate balance after weighting
_________(W.out, m.threshold = .05, disp.v.ratio = TRUE)
```

@@

```{r}
# Merge hand and weightit weights
wdf <- data.frame(hand = lalonde$weights,
                  weightit = get.w(W.out))
# Calculate correlation
cor(____)

# Plot Weights
ggplot(wdf, aes(x=___, y=_____))+
  geom_point()+
  geom_abline(slope=1, lty=2)+
  xlab("Weights computed by hand")+
  ylab("Weights computed by WeightIt")+
  theme_bw()
```

@@

```{r}
# Create CPBS Weights
CPBS.out <-  ______(_____ ~ ____________________, 
			data = lalonde, ATT = TRUE)

@@

# Plot Weights
ggplot(____, aes(x=_____, y=______))+
  geom_point()+
  geom_abline(slope=1, lty=2)+
  xlab("Weights computed by CBPS")+
  ylab("Weights computed by WeightIt")+
  theme_bw()

@@

```{r}
# Model using WeightIt Weights and controlling for race
fit1 <- lm(____ ~ ______, data = lalonde, weights = get.w(W.out))
summary(fit1)

# Model using CBPS Weights and controlling for race
fit2 <- lm(____ ~ ______, data = lalonde, weights = CPBS.out$weights)
summary(fit2)

@@

# Look at balance of demographic variables
bal.tab(______ ~ _____ + _____ + ____ + _____, 
        data = ncp_final, estimand = ______, m.threshold = .05)
```

@@

```{r}
# Create weights
W.out <- weightit(_____ ~ ______ + _____ + ____ + ______,
                  data = _______, estimand = ______, method = "ps")
# Re-check balance with weights
bal.tab(W.out, m.threshold = .05, disp.v.ratio = TRUE)
```

@@

```{r}
# without any adjustment
# without any adjustment
tmod1 <- lm(conservative ~ treat + interest + as.factor(gender) + 
              as.factor(region)+ as.factor(edu) + as.factor(yob) , ncp_final)

@@

# Create survey weights using svydesign
design <- ________________________

# Estimate model
tmod2 <- svyglm(____________________)
# 95% CI
summ(tmod2, confint = TRUE) 
```

@@

# Calculate weights with survey weights
W.out <- weightit(_______________________, s.weights="weights")
# Check balance
bal.tab(W.out, m.threshold = .05, disp.v.ratio = TRUE, un=TRUE)
```

@@

# Estimate the model using lm and specifying weights
tmod3 <- lm(____________________, weights = att.weights)

@@

Report all models in the same table using stargazer (make sure to specify html document). What is your conclusion?

@@

stargazer(_____, _____, _____, type="html",
          covariate.labels = c("Primed",
                               "Political Interest",
                               "Female",
                               "Østlandet",
                               "Sørlandet",
                               "Vestlandet",
                               "Trøndelag",
                               "Nord-Norge",
                               "Completed Upper Secondary Education",
                               "Completed University/ College Education",
                               "Born between 1940-1949",
                               "Born between 1950-1959",
                               "Born between 1960-1969",
                               "Born between 1970-1979",
                               "Born between 1980-1989",
                               "Born in or after 1990",
                               "Intercept"),
          se=list(NULL, NULL, corr_se),
          column.labels = c("No Weights OLS", "PS Weights SWLS", "PS/NCP Weights SWLS"),
          star.cutoffs = c(.10,.05,.01,.001),
          star.char = c("+","*","**","***"),
          column.sep.width = "10pt",
          notes = c("p<.10+, p<.05*, p<.01**, p<.001***"),
          single.row = TRUE,
          notes.append=FALSE)
```

>>>>

---
title: 'Lab 13: Covariate Balancing and CBPS: Answers'
author: "Eric Parajon with code adapted from Colin Case"
output:
  pdf_document: default
  html_document: default
header-include:
- \usepackage{amsbsy}
- \usepackage{amsmath}
- \usepackage{amssymb}
- \DeclareMathOperator*{\argmin}{argmin} % thin space, limits underneath in displays
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE)
```

@@

pacman::p_load(WeightIt,
               cobalt,
               tidyverse,
               stargazer,
               survey,
               jtools,
               CBPS,
               lmtest,
               sandwich)

# Load dataset Lalonde from cobalt package
data('lalonde', package = 'cobalt')

# Evaluate covariate balance on age, educ, married, nodegree, re74, and re75
bal.tab(treat ~ age + educ + married + nodegree + re74 + re75,
        data = lalonde, estimand = "ATT", m.threshold = .05)

@@

```{r}
# Estimate glm predicting treatment status
ps.mod <- glm(treat~ age + educ + married + nodegree + re74 + re75, 
              data = lalonde, family = "binomial")
# Create predictions
ps <- predict(ps.mod, type = "response")
# View propensity scores
head(ps)
```

@@

```{r}
# Estimate and View model without weights
lalonde_model_noW <- lm(re78 ~ treat + race, data=lalonde)
summary(lalonde_model_noW)
# Estimate and view model with weights
lalonde_model_w <- lm(re78 ~ treat + race, data = lalonde, weights = weights)
summary(lalonde_model_w)
```

@@

```{r}
# Use weightit to calculate weights
W.out <- weightit(treat ~ age + educ + married + nodegree + re74 + re75,
        data = lalonde, estimand = "ATT", method = "ps")
W.out
```

@@

```{r}
# Re-examine covariate balance after weighting
bal.tab(W.out, m.threshold = .05, disp.v.ratio = TRUE)
```

@@

```{r}
# Merge hand and weightit weights
wdf <- data.frame(hand = lalonde$weights,
                  weightit = get.w(W.out))
# Calculate correlation
cor(wdf)

# Plot Weights
ggplot(wdf, aes(x=hand, y=weightit))+
  geom_point()+
  geom_abline(slope=1, lty=2)+
  xlab("Weights computed by hand")+
  ylab("Weights computed by WeightIt")+
  theme_bw()
```

@@

```{r}
CPBS.out <-  CBPS(treat ~ age + educ + married + nodegree + re75 + re74, 
			data = lalonde, ATT = TRUE)

@@

# Plot Weights
ggplot(wdf, aes(x=cbps, y=weightit))+
  geom_point()+
  geom_abline(slope=1, lty=2)+
  xlab("Weights computed by CBPS")+
  ylab("Weights computed by WeightIt")+
  theme_bw()

@@

```{r}
# Model using WeightIt Weights
fit1 <- lm(re78 ~ treat + race, data = lalonde, weights = get.w(W.out))
summary(fit1)

# Model using CBPS Weights
fit2 <- lm(re78 ~ treat + race, data = lalonde, weights = CPBS.out$weights)
summary(fit2)

@@

# Look at balance of demographic variables
bal.tab(treat~ gender + region + edu + yob, 
        data = ncp_final, estimand = "ATT", m.threshold = .05)
```

@@

```{r}
# Create weights
W.out <- weightit(treat ~ gender + region + edu + yob,
                  data = ncp_final, estimand = "ATT", method = "ps")
# Re-check balance with weights
bal.tab(W.out, m.threshold = .05, disp.v.ratio = TRUE)
```

@@

```{r}
# without any adjustment
tmod1 <- lm(conservative ~ treat + interest + as.factor(gender) + 
              as.factor(region)+ as.factor(edu) + as.factor(yob) , ncp_final)

@@

# Create survey weights using svydesign
design <- svydesign(ids = ~1, weights = get.w(W.out),
                 data = ncp_final)

# Estimate model
tmod2 <- svyglm(conservative ~ treat + interest + as.factor(gender) + 
                as.factor(region)+ as.factor(edu) + as.factor(yob), 
                design = design)
# 95% CI
summ(tmod2, confint = TRUE) 
```

@@

# Calculate weights with survey weights
W.out <- weightit(treat ~ gender + region + edu + yob,
                  data = ncp_clean, estimand = "ATT", method = "ps",
                  s.weights="weights")
# Check balance
bal.tab(W.out, m.threshold = .05, disp.v.ratio = TRUE, un=TRUE)
```

@@

# Estimate the model using lm and specifying weights
tmod3 <- lm(conservative ~ treat + interest + as.factor(gender) + 
              as.factor(region)+ as.factor(edu) + as.factor(yob) , 
            data = ncp_clean, weights = att.weights)

@@

5. Report all models in the same table using stargazer (make sure to specify html document). What is your conclusion?

@@

stargazer(tmod1, tmod2, tmod3, type="html",
          covariate.labels = c("Primed",
                               "Political Interest",
                               "Female",
                               "Østlandet",
                               "Sørlandet",
                               "Vestlandet",
                               "Trøndelag",
                               "Nord-Norge",
                               "Completed Upper Secondary Education",
                               "Completed University/ College Education",
                               "Born between 1940-1949",
                               "Born between 1950-1959",
                               "Born between 1960-1969",
                               "Born between 1970-1979",
                               "Born between 1980-1989",
                               "Born in or after 1990",
                               "Intercept"),
          se=list(NULL, NULL, corr_se),
          column.labels = c("No Weights OLS", "PS Weights SWLS", "PS/NCP Weights SWLS"),
          star.cutoffs = c(.10,.05,.01,.001),
          star.char = c("+","*","**","***"),
          column.sep.width = "10pt",
          notes = c("p<.10+, p<.05*, p<.01**, p<.001***"),
          single.row = TRUE,
          notes.append=FALSE)
```
